	%\documentclass{article}

\documentclass[a4paper,12pt]{article}
\usepackage{anysize}
\usepackage{array}
\usepackage[top=10mm, left=15mm, right=2mm, bottom=15mm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\usepackage{color,graphicx}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{stmaryrd}
\usepackage{multirow}

\hypersetup{
    bookmarks=true,        % show bookmarks bar?
    unicode=false,         % non-Latin characters in Acrobat's bookmarks
    pdftoolbar=true,       % show Acrobat's toolbar?
    pdfmenubar=true,       % show Acrobat's menu?
    pdffitwindow=true,     % page fit to window when opened
    pdftitle={CV - Deven Patel}, % title
    pdfauthor={Deven Patel},     % author
    pdfsubject={Resume},   % subject of the document
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=magenta,     % color of internal links
    citecolor=blue,        % color of links to bibliography
    filecolor=magenta,     % color of file links
    urlcolor=cyan          % color of external links
}

\definecolor{titleColor}{rgb}{0.85, 0.85, 0.85}

% \usepackage{fullpage}
%%\addtolength{\oddsidemargin}{-.175in}
%	\addtolength{\evensidemargin}{-.875in}
%\addtolength{\topmargin}{-.875in}%
%	\addtolength{\textheight}{1.75in}
\begin{document}

%{\qquad \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\}
%{1 \\2 \\3 \\4 \\5 \\6 \\7 \\8\\ 9\\ }
\title{Deven Patel}
\date{}
\maketitle


%%%%%%%%%%% Experience
\Large\textbf{Professional Experience}
\tiny
\begin{center}
\line(1,0){550}
\end{center}
%\colorbox{titleColor}{\parbox{6.7in}{\textbf{Image Processing Consultant (Binaryveda :2014-)}}}
\large
\textbf{Image Processing Consultant} \normalsize\hspace{5cm}(Binaryveda :2014-)

\begin{itemize}
\item Developed an image matching and recognition feature for a photo-printer app. The application uses algorithms from computer vision as well as machine learning to scan photographs and search from existing database. 
\item Developed a python based basic image analysis application. The application could segment natural  images into different components. It could also do face detection, pedestrian detection and segment images into super-pixels. 
\item Designed and implemented a speech analysis application in python using Google's Web Speech API. 
\end{itemize}

\bigskip

%\colorbox{titleColor}{\parbox{6.7in}{\textbf{Assistant Professor (RGIT :2012-2014)}}}
\large
\textbf{Assistant Professor}\normalsize\hspace{6cm}(RGIT :2012-2014)

\begin{itemize}
\item Guided  two image processing based projects: Gesture Recognition, Head Tracking.   
\item Conducted courses and designed  lab experiments/assignments for courses
like DSP, Image Processing and Random Signal Analysis  
\item Introduced the use of OpenCV for Image Processing laboratory
\end{itemize}
\bigskip
%\item Teaching Assistant - Courses: Image Processing, Computer Vision, Computational Methods.
%\item Teaching Assistant - Lab    :, , 
%\item Conducted a session of Matlab for professionals  workshop at Vidyalankar Institute of Technology 
%\end{description}

%%%%%%%%%%%% RESEARCH
\colorbox{titleColor}{\parbox{6.7in}{\textbf{Research (IIT-B :2008-2012)}}}
%\textit{Synopsis} Multiple-frame SR use the sub-pixel shifts between multiple
%low resolution images of the same scene. They create an improved resolution
%image using information from all low resolution images, and the created higher
%resolution images are better descriptions of the scene. Using Optical-flow the
%SR-technique is generalised by freeing it from the traditional global motion
%assumption. 
\begin{itemize}
\item Using multiple images of the same scene we try to super-resolve or obtain
high resolution image of the scene. This technique is called Super-Resolution
 \item This method is also then used for
converting SDTV image to HDTV image.
\item  Using Optical-flow the SR-technique is generalised by freeing it from the traditional global motion assumption. 
\end{itemize}
\bigskip

\colorbox{titleColor}{\parbox{6.7in}{\textbf{Technical Skills}}}
\begin{description}
\item [Operating System :] Linux/Unix, Windows, Android
\item [Programming      :]  C/C++, Python, Java, Linux Scripting 
\item [Tools            :] Matlab, Octave, OpenCV, Eclipse, \LaTeX 
\end{description}
\bigskip

\colorbox{titleColor}{\parbox{6.7in}{\textbf{Publications}}}
\begin{description}
\item   Deven Patel, Subhasis Chaudhuri: Performance Analysis for Image Super-Resolution Using Blur as a Cue. IEEE-ICAPR 2009
%\item \textit{Submitted} : SDTV to HDTV conversion using Optical-flow to IEEE Transactions on Consumer Electronics.
\end{description}
\bigskip


\colorbox{titleColor}{\parbox{6.7in}{\textbf{ Contact Information}}}
\begin{description}
\item 
\begin{tabular}{ll}%DOB &: 26-03-1982\\
%Address&: At.Po Kotlaw ``Abilasha'' \\&\hspace{7pt}Killa Pardi, Dist Valsad;\\&\hspace{7pt}Gujarat.\\&\hspace{7pt}PIN-396125\\
 deven.patel2@gmail.com \\
 09819482499
\end{tabular}
\end{description}
\end{document}
